Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-04-01 Paper/paper.tex
adding captions for multiple obs figs

\pagebreak
\newpage
\FloatBarrier
\section{Combining observations: looking forward with Advanced LIGO}\label{s1:multiple_observations}
% 
% 
\begin{figure*}
\centering    
\includegraphics[width=1.\columnwidth]{plots/pdfLambda_vs_N_L800.pdf}
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L800.pdf}
\caption{HELLO
}
\label{fig:TT_Lambda_vs_N_L800_CI90_0}
\end{figure*}
%
% 
\begin{figure*}
\centering    
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L2000.pdf}
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L1500.pdf}\\
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L1000.pdf}
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L500.pdf}
\caption{HELLO
}
\label{fig:TT_Lambda_vs_N_L500_2000_CI90_0}
\end{figure*}
%
% 
% \begin{figure}
% \centering    
% \includegraphics[width=1.\columnwidth]{plots/FillBetweenRelErrorBarsLambda_vs_NShifted_AllLambda.pdf}
% \caption{HELLO
% }
% \label{fig:TT_Lambda_vs_N_L500_2000_CI90_0_AllInOne}
% \end{figure}
%
% 
\begin{figure*}
\centering    
\includegraphics[width=1.\columnwidth]{plots/RelErrorLambdaMedian_vs_N.pdf}
\includegraphics[width=1.\columnwidth]{plots/LambdaCIWidths_vs_N.pdf}
\caption{HELLO
}
\label{fig:TT_LambdaError_vs_N_L500_2000_CI90_0}
\end{figure*}
%

% 
\begin{figure}
\centering    
\includegraphics[width=1.\columnwidth]{plots/LambdalErrorBars_vs_Lambda_N49_Log.pdf}
\caption{HELLO
}
\label{fig:TT_Lambda_vs_Lambda_L500_2000_CI90_0_AllInOne}
\end{figure}
%

>>>>

\pagebreak
\newpage
\FloatBarrier
\section{Combining observations: looking forward with Advanced LIGO}\label{s1:multiple_observations}
\includegraphics[width=1.\columnwidth]{plots/pdfLambda_vs_N_L800.pdf}
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L800.pdf}
\caption{{\it Left}:  Posterior probability distributions for $\lambdans$
and associated $90\%$ confidence intervals, shown as a function of number of events 
accumulated $N$.
{\it Right}: Filled-region plots showing the median and $90\%$ confidence intervals
for $\lambdans$, as a function of the number of observed events $N$.
 Shown are two independent filled regions. 
 One in green shows the recovered confidence interval
 for $\lambdans$ (on the left y-axis), normalized by its true value,
 as a function of the 
 number of observed events $N$. The recovered median is shown by the
 green line-circled curve. The pair of horizontal green dashed (dotted)
 lines show the $\pm 50\%$ ($\pm 25\%$) symmetric error bounds around
 the true $\lambdans$ value, which is shown at y-value $=1$ by definition.
 The second filled region, in grey, shows the recovered
 confidence interval for neutron star compactness, without normalizing.
 The corresponding y-values are shown on the *right* y-axis. The horizontal grey
 dashed line traces the true value of $\lambdans$, and is what we expect
 the filled region to approach with increasing number of observations.
 Finally, the grey dotted lines are contours of $1/\sqrt{N}$, drawn to aid the eye.
\label{fig:TT_Lambda_vs_N_L800_CI90_0}
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L2000.pdf}
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L1500.pdf}\\
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L1000.pdf}
\includegraphics[width=1.\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L500.pdf}
\caption{Filled-region plots showing the median and $90\%$ confidence intervals
for $\lambdans$ measurement, as a function of the number of observed events $N$.
Different panels correspond to different injected $\lambdans$ values, which is shown
in their title. In each panel are shown two independent filled regions. 
 One in green shows the recovered confidence interval
 for $\lambdans$ (on the left y-axis), normalized by its true value,
 as a function of the 
 number of observed events $N$. The recovered median is shown by the
 green line-circled curve. The pair of horizontal green dashed (dotted)
 lines show the $\pm 50\%$ ($\pm 25\%$) symmetric error bounds around
 the true $\lambdans$ value, which is shown at y-value $=1$ by definition.
 The second filled region, in grey, shows the recovered
 confidence interval for neutron star compactness, without normalizing.
 The corresponding y-values are shown on the *right* y-axis. The horizontal grey
 dashed line traces the true value of $\lambdans$, and is what we expect
 the filled region to approach with increasing number of observations.
 Finally, the grey dotted lines are contours of $1/\sqrt{N}$, drawn to aid the eye.
\label{fig:TT_Lambda_vs_N_L500_2000_CI90_0}
% \begin{figure}
% \includegraphics[width=1.\columnwidth]{plots/FillBetweenRelErrorBarsLambda_vs_NShifted_AllLambda.pdf}
% \caption{HELLO
% \label{fig:TT_Lambda_vs_N_L500_2000_CI90_0_AllInOne}
% \end{figure}
\includegraphics[width=1.\columnwidth]{plots/LambdaCIWidths_vs_N.pdf}
\includegraphics[width=1.\columnwidth]{plots/RelErrorLambdaMedian_vs_N.pdf}
\caption{{\it Left}: In the main panel is shown the width of the measured $90\%$ 
confidence interval for $\lambdans$, normalized by its true value,
 as a function of the number of events observed $N$. In the inset, we
 show the same measurement uncertainty, but not normalized, and on a 
 logarithmic axis for $N$ as well.
 From both the inset and the main plot, we find that for the first $3-4$ events
 our measurement is prior limited. As $N$ increases, the uncertainty falls 
 roughly as $1/\sqrt{N}$ with intermittent loud signals causing more rapid 
 (than $1/\sqrt{N}$) narrowing of the confidence interval.
 {\it Right}: This figure shows the fractional difference between the median
 recovered value from the posterior probability distribution for $\lambdans$
 as a function of $N$. Different curves correspond to different injected values
 of $\lambdans$, and are shaded from light to dark in direct proportion. 
 The horizontal dashed brown line marks $10\%$ deviation of the median from the 
 true value.
We find that within $\approx 10$ detections, the median measured value for
$\lambdans$ would estimate the true value for the star with the remarkable 
accuracy of $10\%$.
\label{fig:TT_LambdaError_vs_N_L500_2000_CI90_0}

% 
\begin{figure}
\centering    
\includegraphics[width=1.\columnwidth]{plots/LambdalErrorBars_vs_Lambda_N49_Log.pdf}
\caption{This figure shows the relative uncertainty in the measurement of $\lambdans$,
as a function of $\lambdans$ itself. The drawn curves are cumulative, in the sense 
that the $N=n$ curve includes information from all of the first $n$ observed events.
Those corresponding to the first $N\leq 5$ events are shown in fading shades of red,
with the ones for higher value of $N$ being shown in grey (going from light to dark in
proportion to $N$).
Green dash-dotted lines are contours of $y=x^{-(1+1/5)}$.
% 
\prayush{We note that the measurement uncertainty from a population follows the
equation for the green lines.}
% 
}
\label{fig:TT_Lambda_vs_Lambda_L500_2000_CI90_0_AllInOne}
\end{figure}
%
